\Large Carryover effects in free recall reveal how past experiences influence memories of future experiences

### 2023-01-17 paper/main.tex
corrected error in methods section (describing how embeddings were computed)

\textbf{JRM NOTE: REMINDER TO CHECK THIS PARAGRAPH AGAINST ANALYSIS CODE FOR
ACCURACY...} Following some of our prior work~\citep{HeusEtal18a, HeusEtal21},
we use low-dimensional embeddings to help visualize how participants' memory
fingerprints change across lists
(Figs.~\ref{fig:fingerprint-trajectories}A,~\fingerprintTrajectoryRandom A). To
compute a shared embedding space across participants and experimental
conditions, we concatenated the full set of fingerprints (across all lists,
participants, and experimental conditions) to create a large matrix with
number-of-lists $\times$ number-of-participants rows and seven columns (one for
each feature clustering score, plus an additional temporal clustering score
column). We used principal components analysis to project the seven-dimensional
observations into a two-dimensional space (using the two principal components
that explained the most variance in the data). For two visualizations
(Figs.~\ref{fig:fingerprint-trajectories}B,~and~\fingerprintTrajectoryRandom B)
we computed an additional set of two-dimensional embeddings for participants'
\textit{average} fingerprints (i.e., across lists within a given group of
lists-- early or late). For those visualizations we averaged across the rows
(for each condition and group of lists) in the combined fingerprint matrix
prior to projecting it into the shared two-dimensional space. This yielded a
single two-dimensional coordinate for each \textit{list group}, rather than for
each individual list. We used these embeddings solely for visualization. All
statistical tests were carried out in the original (seven-dimensional) feature
spaces.

>>>>

Following some of our prior work~\citep{HeusEtal18a, HeusEtal21}, we use
low-dimensional embeddings to help visualize how participants' memory
fingerprints change across lists
(Figs.~\ref{fig:fingerprint-trajectories}A,~\fingerprintTrajectoryRandom A). To
compute a shared embedding space across participants and experimental
conditions, we concatenated the full set of fingerprints (across all list
groupings, participants, and experimental conditions) to create a large matrix
with number-of-list-groupings $\times$ number-of-participants rows and seven
columns (one for each feature clustering score, plus an additional temporal
clustering score column). We used principal components analysis to project the
seven-dimensional observations into a two-dimensional space (using the two
principal components that explained the most variance in the data). For two
visualizations
(Figs.~\ref{fig:fingerprint-trajectories}B,~and~\fingerprintTrajectoryRandom B)
we computed an additional set of two-dimensional embeddings for the
\textit{average} fingerprints across lists within a given list grouping (i.e.,
early or late). For those visualizations, we averaged across the rows (for each
condition and group of lists) in the combined fingerprint matrix prior to
projecting it into the shared two-dimensional space. This yielded a single
two-dimensional coordinate for each \textit{list group}, rather than for each
individual list. We used these embeddings solely for visualization. All
statistical tests were carried out in the original (seven-dimensional) feature
spaces.
